Effectful Semantics for Substructural SSA

### 2023-11-14 pldi24/paper.tex
Tap

\TODO{some text about each metatheoretic judgement}

@@

>>>>

@@

In particular, the judgement \(\issubst{\gamma}{\Theta}{\Gamma}\) says that
\(\gamma\), which is taken to be a map from variable names to expressions, is a
valid substitution taking \(\Theta\) to \(\Gamma\). What this means is that, for
each variable \(\thyp{x}{A}{q}\) in \(\Gamma\), \(\gamma(x)\) can be interpreted
as a \textit{pure} term of type \(A^q\) in a subcontext of \(\Theta\), such that
when this is done for all \(\thyp{x}{A}{q} \in \Gamma\) any non-affine variables
in \(\Theta\) are used up: this is described formally via the typing rules
\rle{subst-nil}, which says that any function \(\gamma\) takes the empty context
to itself, and \rle{subst-cons}, which says that if \(\gamma\) takes
\(\Theta_\Gamma\) to \(\Gamma\), \(\hasty{\Theta_x}{1}{\gamma(x)}{A}{q}\), \(q
\subseteq \ms{lin}(\Theta_x)\) (to avoid necessating the duplication/discarding
of substructural variables), and \(\Theta\) splits into \(\Theta_\Gamma\) and
\(\Theta_x\), then \(\issubst{\gamma}{\Theta}{\Gamma, \thyp{x}{A}{q}}\).

\TODO{some text about label substitution operations}

\TODO{shuffle subst/lsubst and then ops?}
